---
title: '`r params$crop`'
output:
  word_document: 
    fig_height: 7
    fig_width: 14
    toc: yes
  html_notebook: default
  pdf_document: default
params:
  crop: nothing
---



## Load the working packages
```{r message=FALSE, warning=FALSE}
library(AgroR)
library(tidyverse)
library(agricolae)
library(lme4)
library(emmeans)
library(reshape)
library(reshape2)
library(car)

```



## Load the data

```{r cars, warning=FALSE}
 setwd("~/Code/R/SCASI")
library(tidyverse)
library(skimr)

df <- readxl::read_excel("./input/SCASI_Field_Trials_Data_2022ALL_20230409_Adama_v2.xlsx",sheet = "MergePart2Part1")
# First rows
#knitr::kable(head(df))

# Convert to factor
df$Rep <- as.factor(df$Rep)
df$Treatment <- as.factor(df$Treatment)
df$Woreda <- as.factor(df$Woreda)
```

## Overview of the data
Number of observations and variables:
```{r echo=FALSE}
dim(df)
```

## Extract data per crops
```{r warning=FALSE}
# crop_data
crop_data <- df %>% filter(Plot_crop==params$crop)
```

## Descriptive statistics
### Yield accorss treatments
```{r warning=FALSE}
yield_trt_summary<- crop_data %>% group_by(Treatment) %>% summarize(across(.cols = c(GY_kg_ha,SY_kg_ha),list(min=min,max=max,mean=mean,sd=sd),na.rm=T,.names = "{.fn}_{.col}"))
knitr::kable(yield_trt_summary)
#yield_trt_summary
#with(crop_data, desc(Treatment, GrainYield, ylab = "Grain Yield ", xlab = "Treatment", ylim = NA))

#boxplot
crop_data %>% select(GY_kg_ha, SY_kg_ha, Treatment) %>% gather(key = "Yields",value= "Value", -Treatment) %>% 
ggplot(aes(x=Treatment,y=Value, fill=Yields)) +
  geom_boxplot() +
  scale_fill_manual(values = c("GY_kg_ha" = "#dfc27d", "SY_kg_ha" = "#80cdc1"), labels=c("Grain", "Stover")) +
  labs(y="Yield (Kg/ha)")+
  theme_bw()+
  theme(legend.title = element_text(size = 18),
        legend.text = element_text(size = 16),
        axis.title = element_text(size = 24),
        axis.text = element_text(size = 20))
```

### Yield accorss locations
```{r warning=FALSE}
yield_location<- crop_data %>% group_by(Woreda) %>% summarize(across(.cols = c(GY_kg_ha,SY_kg_ha),list(min=min,max=max,mean=mean,sd=sd),na.rm=T,.names = "{.fn}_{.col}"))
knitr::kable(yield_location)
#yield_trt_summary
#with(crop_data, desc(Treatment, GrainYield, ylab = "Grain Yield ", xlab = "Treatment", ylim = NA))

#boxplot
crop_data %>% select(GY_kg_ha, SY_kg_ha, Woreda) %>% gather(key = "Yields",value= "Value", -Woreda) %>% 
ggplot(aes(x=Woreda,y=Value, fill=Yields)) +
  geom_boxplot() +
  scale_fill_manual(values = c("GY_kg_ha" = "#d01c8b", "SY_kg_ha" = "#4dac26"), labels=c("Grain", "Stover")) +
  labs(y="Yield (Kg/ha)")+
  theme_bw()+
  theme(legend.title = element_text(size = 18),
        legend.text = element_text(size = 16),
        axis.title = element_text(size = 24),
        axis.text = element_text(size = 20))
```


### Yield accorss locations and treatments
* Summary table 
```{r warning=FALSE}
yield_location_trt<- crop_data %>% select(GY_kg_ha, SY_kg_ha, Woreda,Treatment) %>% group_by(Woreda,Treatment) %>% summarize(across(.cols = c(GY_kg_ha, SY_kg_ha),list(min=min,max=max,mean=mean,sd=sd),na.rm=T,.names = "{.fn}_{.col}"))
knitr::kable(yield_location_trt)
#yield_trt_summary
#with(crop_data, desc(Treatment, GrainYield, ylab = "Grain Yield ", xlab = "Treatment", ylim = NA))

```


* Grain 
```{r message=FALSE, warning=FALSE}
#boxplot
crop_data %>% select(GY_kg_ha, Woreda,Treatment) %>% 
ggplot(aes(x=Treatment,y=GY_kg_ha, fill=Woreda)) +
  geom_boxplot() +
  scale_fill_brewer(palette = "Set1") +
  labs(y="Grain Yield (kg/ha)")+
  theme_bw()+
  theme(legend.title = element_text(size = 18),
        legend.text = element_text(size = 16),
        axis.title = element_text(size = 24),
        axis.text = element_text(size = 20))
```

* Stover 
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
#boxplot
crop_data %>% select(SY_kg_ha, Woreda,Treatment) %>% 
ggplot(aes(x=Treatment,y=SY_kg_ha, fill=Woreda)) +
  geom_boxplot() +
  scale_fill_brewer(palette = "Set2") +
  labs(y="Grain Yield (kg/ha)")+
  theme_bw()+
  theme(legend.title = element_text(size = 18),
        legend.text = element_text(size = 16),
        axis.title = element_text(size = 24),
        axis.text = element_text(size = 20))
```



## Factorial analysis
```{r warning=FALSE}

# Analysis of variance

#
if (length(unique(crop_data$Woreda))<=1) {
  model <- lm(GY_kg_ha~ Treatment, data=crop_data)
  anova(model)
} else {
  model <- lm(GY_kg_ha~ Treatment + Woreda + (Treatment:Woreda) + (Woreda:Rep),data=crop_data)
  anova(model)
}
```

## Posthoc test
```{r warning=F}

# Compute the estimated marginal means
emmeans_result <- emmeans(model, ~ Treatment)

# Perform pairwise comparisons using Tukey's adjustment
pairwise_result <- pairs(emmeans_result, adjust = "tukey")

# Display the pairwise comparisons
knitr::kable(pairwise_result)
```
```{r warning=FALSE}
#plot(pairwise_result, pch = "*", cex = 1.5)
as_tibble(pairwise_result) %>% 
ggplot(aes(x=estimate,y=contrast)) +
  geom_point(shape=23, size = 3, fill = "red") +
  geom_errorbar(aes(xmin = estimate - SE, xmax = estimate + SE),
                width = 0.2) +
  labs(x = "Estimate", y = "Contrast")+
  theme_bw()+
  theme(axis.title = element_text(size = 16),
        axis.text = element_text(size = 11))
```

## Best treatment per location
### For every woreda, what are the 3 best treatment?
* Grain
```{r warning=FALSE}
best_comb<-yield_location_trt %>% select(Woreda, Treatment, mean_GY_kg_ha) %>% 
  group_by(Woreda) %>%
  slice_max(mean_GY_kg_ha, n=3)
knitr::kable(best_comb)
```
* Stover
```{r}
best_comb<-yield_location_trt %>% select(Woreda, Treatment, mean_SY_kg_ha) %>% 
  group_by(Woreda) %>%
  slice_max(mean_SY_kg_ha, n=3)
knitr::kable(best_comb)
```


